Demographic Groups with Stronger Biden Support in the Election Races

### 2024-03-17 paper/paper.qmd
Update paper.qmd

Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}. Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes. It will talk about how the model is set up and model justification. In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model. Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language `R`[@citeR] . The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].

>>>>

Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in Section 2. Following that, our estimand is the probability that an individual voted for Biden or Trump based on three characteristics; their gender, race, and ownership of a gun. The reason for this choice will be further examined in Section 3. Section 3 introduces the model designed to generalize patterns and forecast election outcomes. It will talk about how the model is set up and model justification. In Section 4, I will talk about the predicted results derived from the model, this includes the result of the model. Lastly, Section 5 contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language R (R Core Team 2022). The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al. 2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
2024).
